## SENSITIVITY MODEL FIGURES

(ref:fig-sens-variance-en) Spawning biomass for the base model and sensitivity group 1.

(ref:fig-sens-variance-fr) French here

```{r fig-sens-variance, fig.cap = ifelse(fr(), "(ref:fig-sens-variance-fr)", "(ref:fig-sens-variance-en)")}
plot_biomass_mcmc(sens_models[[1]],
                  angle_x_labels = TRUE,
                  text_title_size = NULL,
                  show_bo_lines = TRUE,
                  line_width = 0.5,
                  point_size = 1.5,
                  ylim = c(0, 80000))
```

(ref:fig-sens-variance-rel-en) Relative spawning biomass for the base model and sensitivity group 1.

(ref:fig-sens-variance-rel-fr) French here

```{r fig-sens-variance-rel, fig.cap = ifelse(fr(), "(ref:fig-sens-variance-rel-fr)", "(ref:fig-sens-variance-rel-en)")}
plot_biomass_mcmc(sens_models[[1]],
                  rel = TRUE,
                  angle_x_labels = TRUE,
                  text_title_size = NULL,
                  show_bo_lines = TRUE,
                  line_width = 0.5,
                  point_size = 1.5,
                  ylim = c(0, 1.3))
```

(ref:fig-sens-steepness-prior-en) Priors and posteriors for the base model and sensitivity model 1.

(ref:fig-sens-steepness-prior-fr) French caption here

```{r sens-steepness-prior, fig.cap = ifelse(fr(), "(ref:fig-sens-steepness-prior-fr)", "(ref:fig-sens-steepness-prior-en)"), out.width = "100%"}
plot_priors_posts_mcmc(sens_models[[1]][[2]],
                       param_rm = c("sel",
                                    "bo",
                                    "tau",
                                    "sigma",
                                    "log_m_sex1",
                                    "log_m_sex2",
                                    "so", "beta", "phie"))
```

(ref:fig-sens-q-q-en) Catchability estimates for the base model and sensitivity group 1.

(ref:fig-sens-q-q-fr) French here

```{r fig-sens-q-q, fig.cap = ifelse(fr(), "(ref:fig-sens-q-q-fr)", "(ref:fig-sens-q-q-en)")}
plot_q_mcmc(sens_models[[1]],
            leg_loc = c(0.3, 0.9),
            gear = NULL)
```

(ref:fig-sens-sel-eq-mat-vuln-en) Spawning biomass and vulnerable biomass for the base model and sensitivity group 1.

(ref:fig-sens-sel-eq-mat-vuln-fr) French here

```{r fig-sens-sel-eq-mat-vuln, fig.cap = ifelse(fr(), "(ref:fig-sens-sel-eq-mat-vuln-fr)", "(ref:fig-sens-sel-eq-mat-vuln-en)")}
plot_vuln_mcmc(sens_models[[1]][[2]],
               angle_x_labels = TRUE,
               leg_loc = c(0.1, 0.95),
               xlim = c(1997, 2021),
               ylim = c(0, 25000))
```

(ref:fig-sens-selex-index-fits-en) Index fits for the base model and sensitivity group 1.

(ref:fig-sens-selex-index-fits-fr) French here

```{r fig-sens-selex-index-fits, fig.cap = ifelse(fr(), "(ref:fig-sens-selex-index-fits-fr)", "(ref:fig-sens-selex-index-fits-en)")}
# plot_index_mcmc(sens_models[[1]],
#                 type = "fits",
#                 surv_index = survey_index,
#                 leg_loc = c(0.1, 0.8),
#                 text_title_size = NULL)
# 
```

(ref:fig-sens-qcs-tv-en) Selectivity for sensitivity group 1.

(ref:fig-sens-qcs-tv-fr) French here

```{r fig-sens-qcs-tv, fig.cap = ifelse(fr(), "(ref:fig-sens-qcs-tv-fr)", "(ref:fig-sens-qcs-tv-en)")}
plot_selex_mcmc(sens_models[[1]][[2]], show_maturity = FALSE)
```
\clearpage
